
\printbibliography[title=Publications]


\section{Journal Papers}
\journalpaperlist{

\entrypaper{\meinpaper, Ana Oliveira da Costa, Andrew Wintenberg, Ezio Bartocci, Borzoo Bonakdarpour}
{Gray-box Runtime Enforcement of Hyperproperties}
{Acta Informatica (2025) To appear.}
}

% Can instead manually enter publications as shown:
\section{Conference Papers}
\conferencepaperlist{


\entrypaper{\meinpaper, Arshia Rafieioskouei, Borzoo Bonakdarpour}
{HypRL: Reinforcement Learning of Control Policies for Hyperproperties}
{Annual Conference on Neural Information Processing Systems (NeurIPS'25), to appear.}

	
\entrypaper{Raven Beutner, \meinpaper, Borzoo Bonakdarpour, and Bernd Finkbeiner}
{Syntax-Guided Automated Program Repair For Hyperproperties}
{International Conference on Computer Aided Verification (CAV'24), Montreal, Canada.}
%%%	
\entrypaper{\meinpaper, Borzoo Bonakdarpour, Bernd Finkbeiner, and César Sánchez}
{Bounded Model Checking for Asynchronous Hyperproperties}
{International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS'23), Paris, France.}
%%%
\entrypaper{\meinpaper, César Sánchez, Sarai Sheinvald, and Borzoo Bonakdarpour}
{Efficient Loop Conditions for Bounded Model Checking Hyperproperties}
{International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS'23), Paris, France.}
%%%
\entrypaper{\meinpaper, Borzoo Bonakdarpour, Eunsuk Kang, and Stavros Tripakis}
{Mapping Synthesis for Hyperproperties}
{IEEE International Symposium on Computer Security Foundations (CSF'22/FLoC'22), Haifa, Israel.}
%%%	
\entrypaper{\meinpaper, César Sánchez, and Borzoo Bonakdarpour}
{Bounded Model Checking for Hyperproperties}
{International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS'21), Luxembourg, Luxembourg.}

}





\section{arXiv Preprints}
\arxivpaperlist{

\entrypapertobe{\meinpaper, Borzoo Bonakdarpour, and César Sánchez}
{HyperQB: A QBF-Based Bounded Model Checker for Hyperproperties \text{(v5)}}

\entrypapertobe{\meinpaper, Yu Wang, Borzoo Bonakdarpour, Miroslav Pajic}
{Multi-Agent Path Planning with Hyperproperties \text{(v1)}} {}

}


% \section{Under Review Papers}
% \underreviewpaperlist{

% \entrypapertobe{\meinpaper, Arshia Rafieioskouei, Borzoo Bonakdarpour}
% {HypRL: Reinforcement Learning of Control Policies for Hyperproperties}

% }


%\section{Projects under submission}
%
%\orderedouterlist{
%	
%	\entryproj{\meinpaper, Arshia Rafieioskouei, and Borzoo Bonakdarpour}
%	{Strategies Synthesis using Reinforcement Learning for Hyperproperties} {}
%	
%	\entrypreprint{\meinpaper,  Borzoo Bonakdarpour, Twain Byrnes, Limin Jia}
%	{Syntax-guided Runtime Enforcement for Hyperproperties} {}
%	
%	\entrypreprint{\meinpaper,  Ana Costa, Andrew Wintenburg, Borzoo Bonakdarpour, Ezio Bartocci}
%	{Gray-box Runtime Enforcement for Hyperproperties} {}
%	
%}



\section{Research Fellowships}
\denseouterlist{
	\entrysimple
	{Michigan State University Graduate Research Fellowship}
	{2021, 2022}
	{Received Summer Support for outstanding students selected by MSU CSE department.}
	
	\entrysimple
	{Google Research Fellowship Nomination}
	{2021}
	{Selected as one of the only four nominees selected by MSU College of Engineering.}
}	

\section{Research Award}

\denseouterlist{
	
	\entrysimple{Best Research Poster Award}
	{2024} 
	{Awarded by Michigan State University College of Engineering Graduate Research Symposium.}
	
}




% \section{Links to Personal Website and Publications}
%
%Personal Website: \url{https://tzuhancs.github.io/}\\
%\vspace{2mm}
%{\em Conference Paper 1:} \url{https://tzuhancs.github.io/papers/mapping_synthesis_for_hyperproperties.pdf} \\
%{\em Conference Paper 2:} \url{https://link.springer.com/content/pdf/10.1007/978-3-030-72016-2_6.pdf} \\
%{\em Preprints 1:} \url{https://arxiv.org/pdf/2109.12989.pdf}\\
%{\em Preprints 2:} \url{https://tzuhancs.github.io/papers/multi_agent_planning_with_hyperproperties.pdf}

%\section{Publications}
%\orderedouterlist{
%\entry{S. Petridis, J. Shen, D. Cetin and M. Pantic, "Visual-Only Recognition of Normal, Whispered And Silent Speech", \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), April 2018}}
%}
